Appendix

### 2019-09-24 manuscript/appendix/appendix.Rmd
plot both prediction and true replicates

```{r message = FALSE}
library(tidyverse)
library(patchwork)
library(furrr)
set.seed(12345)
```

@@

```{r}
plan("multisession")
system.time({
  df <- future_map_dfr(1:500, function(reps) sim(may, p), .id = "reps")
})

@@

```{r}
p_det$N <- 3e3
det <- sim(may,p_det) %>% mutate(reps=1)
mean <- df %>% group_by(t) %>% summarise(x = mean(x)) %>% mutate(reps = 1)
```

@@

```{r}
df %>% group_by(reps) %>%
  sample_n(5e2) %>%
  ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.05) +
  geom_line(data = det, color = "blue") + 
  geom_line(data = mean, color = "red")
```

@@

```{r}
means <- df %>% group_by(reps) %>% summarise(ave = mean(x), max = max(x))
lows <- means %>% filter(ave < mean(ave) - 3*sd(ave), max > 120) %>% pull(reps)
```

```{r arima_forecast}
x <- df %>% filter(reps == lows[[1]], t <= 2000) %>% pull(x) %>% as.ts() 
fit <- arima(x)
y <- predict(fit, n.ahead = 1000) %>% as.data.frame()
y <- bind_rows(data.frame(pred = x, se = 0), y)

arima_forecast <- df %>% 
  filter(reps == lows[[1]]) %>% 
  select(t,x) %>%
  bind_cols(y)
```

@@

```{r}
a <- sample(unlist(draws, TRUE), 10)
p$N <- 3e3
posterior_sims <- map_dfr(a, function(a){
  p$a <- a
  sim(may, p)
},
.id = "a")

@@

```{r}
posterior_sims %>% 
  mutate(a = as.numeric(a)) %>% 
  ggplot(aes(t,x, group=a)) + 
  geom_line(alpha = 0.05) 
```

>>>>

```{r message = FALSE}
library(tidyverse)
library(patchwork)
library(ggthemes)
library(furrr)
set.seed(12345)
```

@@

```{r}
plan("multisession")
system.time({
  sim_data <- future_map_dfr(1:500, function(reps) sim(may, p), .id = "reps")
})

@@

```{r}
p_det$N <- 3e3
det <- sim(may,p_det) %>% mutate(reps=1)
mean <- sim_data %>% group_by(t) %>% summarise(x = mean(x)) %>% mutate(reps = 1)
```

@@

```{r}
sim_data %>% group_by(reps) %>%
  sample_n(5e2) %>%
  ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.05) +
  geom_line(data = det, color = "blue") + 
  geom_line(data = mean, color = "red")
```

@@

```{r}
means <- sim_data %>% group_by(reps) %>% summarise(ave = mean(x), max = max(x))
lows <- means %>% filter(ave < mean(ave) - 3*sd(ave), max > 120) %>% pull(reps)
```

```{r arima_forecast}
x <- sim_data %>% filter(reps == lows[[1]], t <= 2000) %>% pull(x) %>% as.ts() 
fit <- arima(x)
y <- predict(fit, n.ahead = 1000) %>% as.data.frame()
y <- bind_rows(data.frame(pred = x, se = 0), y)

arima_forecast <- sim_data %>% 
  filter(reps == lows[[1]]) %>% 
  select(t,x) %>%
  bind_cols(y)
```

@@

```{r}
a <- unname(sample(unlist(draws, TRUE), 100))
p$N <- 1e3
x <- sim_data %>% filter(reps == lows[[1]], t == 2001) %>% pull(x)

p$x0 <- x[[1]]
posterior_sims <- map_dfr(a, function(a){
  p$a <- a
  sim(may, p)
},
.id = "reps")

@@

```{r}
alpha <- 0.1
training_data <- train %>% select(t,x) %>% mutate(reps="1", set = "training", alpha = 1)

true_forecast <- 
  future_map_dfr(1:100, 
                 function(reps) sim(may, p), 
                 .id = "reps"
                 ) %>% 
  mutate(t = t+2000,
         set = "true",
         alpha = alpha) %>% 
  bind_rows(training_data)

predicted_forecast <- posterior_sims %>% 
    mutate(t = t+2000,
           set = "predicted",
           alpha = alpha)
```

```{r}
bind_rows(predicted_forecast, true_forecast) %>% 
  ggplot(aes(t,x)) +
  geom_line(aes(group = interaction(reps, set), col = set), alpha = .05) + 
  geom_line(data = training_data) + 
  scale_color_solarized()
```

```{r}

posterior_sims %>% 
  mutate(a = as.numeric(a), 
         t = t+2000) %>% 
  ggplot(aes(t,x)) + 
  geom_line(aes(group = reps), col = "blue", alpha = 0.05,
            data = true_forecast) + 
  geom_line(aes(group = a), alpha = 0.05, col = "red") + 
  geom_line(data = training_set) 
```
